---
title: "statconvert"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{statconvert}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(statconvert)
```

# Introduction

statconvert is a helpful formatting package that allows the user to easily convert the output of their statistical test into a copy paste-able string. Converting the tabular output of a statistical function into your academic article can often be tedious task and this package streamlines it considerably. Test results are reported according to the APA's standards

# statconvert

This package contains only one namesake function. statconvert is a series of if statements checking the class of the object given to it. Once the function determines which which type of test object it has received, it then calls a specific helper function designed to handle that test and returns a string that you can just copy paste into your word processor.

For example if you wanted to convert the output of a oneway ANOVA test you could use the statconvert function like this

```{r}
data(mtcars)
md <- aov(mpg ~ wt, data = mtcars)
statconvert(md)
```
